Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2011-12-18 ms.tex
Edited abstract according to MV comments
Edited introduction on DM based on MVs comments

A third mechanism for gamma-ray production in a galaxy cluster is self-annihilation of a DM
particle, e.g. a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
the cluster mass is in the form of dark matter. The gamma-ray emissivity from DM annihilations is
proportional to the square of the DM density integrated along the line of sight, making galaxy
clusters potentially good candidates for DM searches \citep{article:EvansFerrerSarkar:2004,
article:BergstromHooper:2006, article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011},
despite their large distances compared to other common targets for DM searches, such as dwarf
spheroidal galaxies \citep{article:Strigari_etal:2007, article:Acciari_etal:2010,
article:Aliu_etal:2009} or the Galactic center \citep{article:Kosack_etal:2004,
article:Aharonian_etal:2006, article:Aharonian_etal:2009b, article:Abramowski_etal:2011}.

>>>>

A third mechanism for gamma-ray production in a galaxy cluster could be self-annihilation of a DM
particle, e.g. a weakly interacting massive particle (WIMP). As already mentioned, about 80\% of
the cluster mass is in the form of dark matter, which makes galaxy clusters interesting targets for
DM searches \citep{article:EvansFerrerSarkar:2004, article:BergstromHooper:2006,
article:PinzkePfrommerBergstrom2009, article:Cuesta_etal:2011} despite their large distances
compared to other common targets for DM searches, such as dwarf spheroidal galaxies
\citep{article:Strigari_etal:2007, article:Acciari_etal:2010, article:Aliu_etal:2009} or the
Galactic center \citep{article:Kosack_etal:2004, article:Aharonian_etal:2006,
article:Aharonian_etal:2009b, article:Abramowski_etal:2011}.
